---
title: "Knobe (2003) Replication Analysis"
author: "Bradley Kennedy"
date: "09/10/2019"
output:
  html_document:
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Current R Version:
```{r, echo=FALSE}
version$version.string
```
Check if required packages need to be installed, if so, install
```{r install packages, results='hide', warning=FALSE, message=FALSE, error=FALSE}
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("plyr")) install.packages("plyr"); library(plyr)
if (!require("tidyr")) install.packages("tidyr"); library(tidyr)
if (!require("reshape2")) install.packages("reshape2"); library(reshape2)
if (!require("polycor")) install.packages("polycor"); library(polycor)
if (!require("corrgram")) install.packages("corrgram"); library(corrgram)
if (!require("esc")) install.packages("esc"); library(esc)
if (!require("psych")) install.packages("psych"); library(psych)
if (!require("lsr")) install.packages("lsr"); library(lsr)
if (!require("ggplot2")) install.packages("ggplot2"); library(ggplot2)
if (!require("dplyr")) install.packages("dplyr"); library(dplyr)
if (!require("Hmisc")) install.packages("Hmisc"); library(Hmisc)
if (!require("rcompanion")) install.packages("rcompanion"); library(rcompanion)
if (!require("beepr")) install.packages("beepr"); library(beepr)
```
Check for package updates from cloud.r-project.org
```{r update packages, results='hide', warning=FALSE, message=FALSE, error=FALSE}
update.packages(ask=FALSE, repos = "https://cloud.r-project.org")
```

***
## Data Wrangling
Import the original data file
```{r import data, warning=FALSE, message=FALSE, error=FALSE}
Data_forCleaning <- read_excel("Data_forCleaning.csv", 
                               col_types = c("text", "text", "text", 
                                             "numeric", "text", "numeric", "text", 
                                             "numeric", "text", "numeric", "text"))
```
Demographic information
```{r}
All_Age <- describe(as.numeric(Data_forCleaning$`4. Please enter your age`))
sd(as.numeric(Data_forCleaning$`4. Please enter your age`), na.rm = TRUE)

Age_bySexIdentity <- describeBy(as.numeric(Data_forCleaning$`4. Please enter your age`),
            group = as.factor(Data_forCleaning$`3. Please enter your gender identity`))
```
Seperate each experimental condition into a seperate dataframe, removing any lines with NA, renaming column names
```{r data wrangling 1}
Exp1_Harm <- select(Data_forCleaning, 4:5)
Exp1_Harm <- na.omit(Exp1_Harm)
names(Exp1_Harm) <- c("Chairman_HA_Blame", "Chairman_HA_Intent")
Exp1_Help <- select(Data_forCleaning, 6:7)
Exp1_Help <- na.omit(Exp1_Help)
names(Exp1_Help) <- c("Chairman_HE_Praise", "Chairman_HE_Intent")
Exp2_Harm <- select(Data_forCleaning, 8:9)
Exp2_Harm <- na.omit(Exp2_Harm)
names(Exp2_Harm) <- c("Lieutenant_HA_Blame", "Lieutenant_HA_Intent")
Exp2_Help <- select(Data_forCleaning, 10:11)
Exp2_Help <- na.omit(Exp2_Help)
names(Exp2_Help) <- c("Lieutenant_HE_Praise", "Lieutenant_HE_Intent")
```
Convert yes no responses to Yes=1 and No=0
```{r data wrangling 2, warning=FALSE}
Exp1_Harm <- mutate_at(Exp1_Harm, vars(2:2), funs(ifelse( . == "Yes",1 , ifelse( . == "No", 0, .))))
Exp1_Harm <- transform(Exp1_Harm, Chairman_HA_Intent = as.numeric(Chairman_HA_Intent))
Exp1_Help <- mutate_at(Exp1_Help, vars(2:2), funs(ifelse( . == "Yes",1 , ifelse( . == "No", 0, .))))
Exp1_Help <- transform(Exp1_Help, Chairman_HE_Intent = as.numeric(Chairman_HE_Intent))
Exp2_Harm <- mutate_at(Exp2_Harm, vars(2:2), funs(ifelse( . == "Yes",1 , ifelse( . == "No", 0, .))))
Exp2_Harm <- transform(Exp2_Harm, Lieutenant_HA_Intent = as.numeric(Lieutenant_HA_Intent))
Exp2_Help <- mutate_at(Exp2_Help, vars(2:2), funs(ifelse( . == "Yes",1 , ifelse( . == "No", 0, .))))
Exp2_Help <- transform(Exp2_Help, Lieutenant_HE_Intent = as.numeric(Lieutenant_HE_Intent))
```

***

## Descriptive Statistics - INTENT - Experiment 1

Harm Condition (How many said Yes, it was intentional)
```{r}
Sum_Yes_Exp1HA <- sum(Exp1_Harm[,2]==1)
Percentage_Yes_Exp1HA <- round((Sum_Yes_Exp1HA/44)*100)
Sum_Yes_Exp1HA
Percentage_Yes_Exp1HA
```
Harm Condition (How many said No, it was NOT intentional)
```{r}
Sum_No_Exp1HA <- sum(Exp1_Harm[,2]==0)
Percentage_No_Exp1HA <- round((Sum_No_Exp1HA/44)*100)
Sum_No_Exp1HA
Percentage_No_Exp1HA
```
Help Condition (How many said Yes, it was intentional)
```{r}
Sum_Yes_Exp1HE <- sum(Exp1_Help[,2]==1)
Percentage_Yes_Exp1HE <- round((Sum_Yes_Exp1HE/44)*100)
Sum_Yes_Exp1HE
Percentage_Yes_Exp1HE
```
Help Condition (How many said No, it was NOT intentional)
```{r}
Sum_No_Exp1HE <- sum(Exp1_Help[,2]==0)
Percentage_No_Exp1HE <- round((Sum_No_Exp1HE/44)*100)
Sum_No_Exp1HE
Percentage_No_Exp1HE
```

## Descriptive Statistics - INTENT - Experiment 2

Harm Condition (How many said Yes, it was intentional)
```{r}
Sum_Yes_Exp2HA <- sum(Exp2_Harm[,2]==1)
Percentage_Yes_Exp2HA <- round((Sum_Yes_Exp2HA/44)*100)
Sum_Yes_Exp2HA
Percentage_Yes_Exp2HA
```
Harm Condition (How many said No, it was NOT intentional)
```{r}
Sum_No_Exp2HA <- sum(Exp2_Harm[,2]==0)
Percentage_No_Exp2HA <- round((Sum_No_Exp2HA/44)*100)
Sum_No_Exp2HA
Percentage_No_Exp2HA
```
Help Condition (How many said Yes, it was intentional)
```{r}
Sum_Yes_Exp2HE <- sum(Exp2_Help[,2]==1)
Percentage_Yes_Exp2HE <- round((Sum_Yes_Exp2HE/44)*100)
Sum_Yes_Exp2HE
Percentage_Yes_Exp2HE
```
Help Condition (How many said No, it was NOT intentional)
```{r}
Sum_No_Exp2HE <- sum(Exp2_Help[,2]==0)
Percentage_No_Exp2HE <- round((Sum_No_Exp2HE/44)*100)
Sum_No_Exp2HE
Percentage_No_Exp2HE
```

***
## Chi Square Tests

Data Prep for Chi Square, moving sum of 'Yes' and sum of 'No' for Exp 1 to seperate table
```{r}
Exp1_Intent <- matrix(c(Sum_Yes_Exp1HA,Sum_Yes_Exp1HE,Sum_No_Exp1HA,Sum_No_Exp1HE), ncol=2)
colnames(Exp1_Intent) <- c('Harm', 'Help')
rownames(Exp1_Intent) <- c('Yes','No')
```
Data Prep for Chi Square, moving sum of 'Yes' for Exp 2 to seperate table
```{r}
Exp2_Intent <- matrix(c(Sum_Yes_Exp2HA,Sum_Yes_Exp2HE,Sum_No_Exp2HA,Sum_No_Exp2HE), ncol=2)
colnames(Exp2_Intent) <- c('Harm', 'Help')
rownames(Exp2_Intent) <- c('Yes','No')
```
Chi Square, test difference between response for Exp1
```{r}
chisq.exp1 <- chisq.test(Exp1_Intent)
chisq.exp1
esc_chisq(chisq = chisq.exp1$statistic,p=chisq.exp1$p.value,totaln = 88 ,es.type = "d")
```
Chi Square, test difference between response for Exp2
```{r}
chisq.exp2 <- chisq.test(Exp2_Intent)
chisq.exp2
esc_chisq(chisq = chisq.exp2$statistic,p=chisq.exp2$p.value,totaln = 88,es.type = "d")
```

## Descriptive Statistics - PRAISE/BLAME

Mean amount of Blame for Harmful SE
```{r}
Mean_Blame <- round(mean(c(Exp1_Harm[,1],Exp2_Harm[,1])),digits=2)
Mean_Blame
```
SD Blame for Harmful SE
```{r}
SD_Blame <- sd(c(Exp1_Harm[,1],Exp2_Harm[,1]))
SD_Blame
```
Mean amount of Praise for Helpful SE
```{r}
Mean_Praise <- round(mean(c(Exp1_Help[,1],Exp2_Help[,1])),digits=2)
Mean_Praise
```
SD Praise for Helpful SE
```{r}
SD_Praise <- sd(c(Exp1_Help[,1],Exp2_Help[,1]))
SD_Praise
```

Create one table of all
```{r}
All_table <- table(c(Exp1_Harm[,1],Exp1_Help[,1],Exp2_Harm[,1],Exp2_Help[,1]),
                   c(Exp1_Harm[,2],Exp1_Help[,2],Exp2_Harm[,2],Exp2_Help[,2]))
All_table <- bind_cols(Exp1_Harm,Exp1_Help,Exp2_Harm,Exp2_Help)
colnames(All_table) <- c("PB","Intent","PB","Intent","PB","Intent","PB","Intent")
All_table <- data.frame(PB = c(All_table[,1],All_table[,3],All_table[,5],All_table[,7]),
                        Intent = c(All_table[,2],All_table[,4],All_table[,6],All_table[,8]))
All_table$Agent <- rep(c("Chairman", "Lieutenant"), each = 88)
All_table$Agent <- as.factor(All_table$Agent)
All_table$Condition <- rep(c("Harm", "Help"), each = 44)
All_table$Condition <- as.factor(All_table$Condition)
All_table$Experiment <- rep(1:2, each=88)
All_table$Experiment <- as.factor(All_table$Experiment)
All_table$Intent <- as.factor(All_table$Intent)
```

Median Praise/Blame ratings for Help/Harm Conditions
```{r}
medianPB_help <- median(c(Exp1_Help[,1],Exp2_Help[,1]))
medianPB_help

medianPB_harm <- median(c(Exp1_Harm[,1],Exp2_Harm[,1]))
medianPB_harm
```

Create Table of Praise/Blame ratings and Harm/Help Intention ratings for Correlation and T test
```{r}
Corr_table <- table(c(Exp1_Harm[,1],Exp1_Help[,1],Exp2_Harm[,1],Exp2_Help[,1]),
                   c(Exp1_Harm[,2],Exp1_Help[,2],Exp2_Harm[,2],Exp2_Help[,2]))
Corr_table <- bind_cols(Exp1_Harm,Exp1_Help,Exp2_Harm,Exp2_Help)
Corr_table <- data.frame(Praise = c(Corr_table[,3],Corr_table[,7]),
                         Blame = c(Corr_table[,1],Corr_table[,5]),
                        PraiseIntent = c(Corr_table[,4],Corr_table[,8]),
                        BlameIntent = c(Corr_table[,2],Corr_table[,6]))
```

## T test to test differences between Praise and Blame ratings
```{r}
PB_ttest <- t.test(Corr_table$Praise,Corr_table$Blame, var.equal = TRUE)
PB_ttest
PB_ttest_effectsize<- cohensD(x=Corr_table$Praise,y=Corr_table$Blame)
PB_ttest_effectsize
cohen.d.ci(PB_ttest_effectsize,n=88,alpha=.05)
```

## Mann-Whitney U test 
Examining the ratings of praise/blame comparing help vs. harm
```{r}
wilcox.test(PB ~ Condition, data = All_table)
```
Mann-Whitney U effect size (r; Small: 0.1, Medium: 0.3, Large: >0.5) 
```{r}
wilcoxonR(x  = All_table$PB, 
          g  = All_table$Condition,
          ci = TRUE)
```
## Mann-Whitney U test 2 
Examining the ratings of praise/blame for intentional yes/no
```{r}
wilcox.test(PB ~ Intent, data = All_table)
```
Mann-Whitney U effect size (r; Small: 0.1, Medium: 0.3, Large: >0.5) 
```{r}
wilcoxonR(x  = All_table$PB, 
          g  = All_table$Intent,
          ci = TRUE)
```

## Correlation between ratings of Praise with help intentionality
```{r}
P.Help_Correlation <- cor.test(Corr_table$Praise,Corr_table$PraiseIntent)
P.Help_Correlation

P.Help_plot <- ggplot(Corr_table, aes(x=PraiseIntent, y=Praise)) + 
                      geom_point() + 
                      geom_smooth(method=lm) +
                      geom_jitter(width = 0.15) +
                      labs(x = "Intentionality Judgement", y = "Praise Rating", 
                          title = "Praise Rating correlation with Help Intentionality") +
                      scale_x_continuous(breaks = c(0,1),labels = c("No", "Yes"))

P.Help_plot
```

## Correlation between ratings of Blame with harm intentionality
```{r}
B.Harm_Correlation <- cor.test(Corr_table$Blame,Corr_table$BlameIntent)
B.Harm_Correlation

B.Harm_plot <- ggplot(Corr_table, aes(x=BlameIntent, y=Blame)) + 
                      geom_point() + 
                      geom_smooth(method=lm) +
                      geom_jitter(width = 0.15) +
                      labs(x = "Intentionality Judgement", y = "Blame Rating", 
                           title = "Blame Rating correlation with Harm Intentionality") +
                      scale_x_continuous(breaks = c(0,1),labels = c("No", "Yes"))

B.Harm_plot
```

##  Correlation between all ratings of Praise/Blame with all intention ratings
```{r}
PB_Correlation <- cor.test(All_table$PB,as.numeric(All_table$Intent))
PB_Correlation
PB_Corr_effectsize <- cohensD(x=All_table$PB,y=as.numeric(All_table$Intent))
cohen.d.ci(PB_Corr_effectsize,n=176,alpha=.05)

PB_plot <- ggplot(All_table, aes(x=as.numeric(Intent), y=PB)) + 
                  geom_point() + 
                  geom_smooth(method=lm) +
                  geom_jitter(width = 0.15) +
                  labs(x = "Intentionality Judgement", y = "Praise/Blame Rating") +
                  scale_x_continuous(breaks = c(1,2), labels = c("No", "Yes"))
PB_plot
```

## Raincloud Plot
```{r}
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
raincloud_theme = theme(text = element_text(size = 12), 
                        axis.title.x = element_text(size = 12), 
                        axis.title.y = element_text(size = 12), 
                        axis.text = element_text(size = 12), 
                        axis.text.x = element_text(vjust = 0.5), 
                        legend.title=element_text(size=12), 
                        legend.text=element_text(size=12), 
                        legend.position = "right", 
                        plot.title = element_text(lineheight=.8, face="bold", size = 16), 
                        panel.border = element_blank(), 
                        panel.grid.minor = element_blank(), 
                        panel.grid.major = element_blank(), 
                        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'), 
                        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

PB_Rain <- ggplot(data = All_table, 
                 aes(y = All_table$PB, x = All_table$Condition, fill = All_table$'Agent')) + 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, trim=TRUE) + 
  geom_point(aes(y = PB, color = All_table$Agent), 
             position = position_jitter(width = .10), size = .5, alpha = 0.8) + 
  expand_limits(x = 3) + guides(fill = FALSE) + guides(color = FALSE) + 
  scale_color_brewer(palette = "Accent") + scale_fill_brewer(palette = "Accent") + 
  coord_flip() + theme_bw() + raincloud_theme + labs(x="Condition") + 
  scale_y_continuous(breaks = seq(0,6,by = 1)) + ylab("Praise/Blame Rating") + 
  stat_summary(fun.data="mean_cl_boot", colour="black", size=.5) +
  facet_wrap(vars(Agent))
PB_Rain
```

## GLM - impact of praise/blame on yes/no response
Replacement of knobes correlation 
```{r}
model1 <- glm(Intent ~ PB, family = binomial, data = All_table)
summary(model1)
confint(model1)
```

## GLM - impact of help/harm condition in exp1 and exp2
Knobes chi square
```{r}
exp1_filter <- All_table$Experiment=="1"
model_exp1 <- glm(Intent ~ Condition, family = binomial, data = All_table[exp1_filter,])
summary(model_exp1)
confint(model_exp1)

exp2_filter <- All_table$Experiment=="2"
model_exp2 <- glm(Intent ~ Condition, family = binomial, data = All_table[exp2_filter,])
summary(model_exp2)
confint(model_exp2)

model2 <- glm(Intent ~ Condition, family = binomial, data = All_table)
summary(model2)
confint(model2)
```

## GLM - interaction between condition and experiment on intentionality
Replacement of knobes correlation 
```{r}
full_model <- glm(Intent ~ Condition*Experiment, family = binomial, data = All_table)
summary(full_model)
confint(full_model)
```

```{r echo=FALSE}
beepr::beep()
```

## End